Estimating Uncertainty for Tipping Points with Deep Learning

### 2022-05-04 manuscript/manuscript.Rmd
Slow going

@@

>>>>

We present forecasts produced by ARIMA models as the model-free analogs to the forecasts made using parameter estimation with MCMC.
In contrast to the ideal case MCMC-based forecasts, ARIMA-based forecasts should serve as a lower limit for the performance of non-mechanistic models.
Since ARIMA models make the assumption that the future will resemble the past via their auto-regressive and moving average components, ARIMA models are not well-suited for tipping point problems.
Uncertainty intervals here are estimated directly from parameters of the model.

@@

Lastly, we examine how deep learning algorithms perform.
Over the past decade, deep learning has become popular for a broad range of challenging predictive tasks.
However, there have been a relatively small number of studies investigating how deep learning methods perform with sequence to sequence time series forecasting [@kao, @lyu, @Du].
Across these studies, it has become established that using memory or attention-based neural networks, and an encoder-decoder architecture is important to improving forecasting performance. 
To investigate these assertions, we examine four models that use a combination of memory, attention and encoder-decoder network architectures.

Many of the common deep learning algorithms are not designed to estimate uncertainty intervals, so it is necessary to consider how deep learning methods can be used for uncertainty estimation. 
With the deep learning models that we present, we take the same approach wherein we set the output of each machine learning model to be the parameters of a poisson distribution.
To estimate the uncertainty interval at any point, we collect samples from the distribution described by the parameters outputted by the model.

A major nuisance with deep learning methods is their instability to hyperparameters and initialization seeds.
We found that for the same set of hyperparameters, we could produce starkly different forecasts if we trained two models with different initialization seeds.
To avoid this instability concern, we ensemble output samples across 5 different initialzation seeds.
In this way, we can regularize for instability for seed initialization.
